\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/ms.tex
recompile

While our findings indicate many areas for further improvement of \gls{llm}-based systems, it is also important to realize that clearly defined metrics have been the key to the progress of many fields of \gls{ml}, such as computer vision.
Although current systems might be far from reasoning like a chemist, our \chembench framework will be a stepping stone for developing systems that might come closer to this goal.

@@

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

>>>>

While our findings indicate many areas for further improvement of \gls{llm}-based systems, such as for agents (more discussion in \Cref{sec:react-environment}), it is also important to realize that clearly defined metrics have been the key to the progress of many fields of \gls{ml}, such as computer vision.
Although current systems might be far from reasoning like a chemist, our \chembench framework will be a stepping stone for developing systems that might come closer to this goal.

@@

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. }
    %Note that the chemical preference questions are the main corpus of the semi-automatically generated group with \variable{output/question_count_per_dir/json_file_counts_preference.txt} questions of the total \variable{output/automatically_generated.txt}.
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}
